---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(regexmagic)
```

# regexmagic

The goal of regexmagic is to provide an automated method for classifying a vector
of strings into groupings based on regex matches. This differs from finding matches to 
a known regex within a vector, rather this helps determine commonalities between 
strings.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jonocarroll/regexmagic")
```

## Example

Given the vector of strings in the (provided) example data, this package 
will determine the groupings by regex

```{r example data}
data(identifiers)
print(identifiers)
```

Within this example data there are 3 distinct patterns, along with 3 identifers which
do not match exactly these patterns (confounders). The goal is to produce a package
which can detect the common patterns and sort the identifiers into the correct
groups.

## Methodology

First, common substrings are identified. These are allowed some tolerance 
by which the identifiers may deviate. By default this is 95% of samples should 
match the pattern.

With the example data, we can detect the common substrings

```{r}
purrr::map(split_by_length(identifiers), find_common_substrings)
```

This has become confused by the confounder in each group which destroys the 
perfect relationship. We can improve this by lowering the tolerance

```{r}
(guess <- purrr::map(split_by_length(identifiers), find_common_substrings, tolerance = 0.9))
```

This successfully identifies the common substrings, but leaves the pattern determining 
the missing parts unknown. Next we need to determine common patterns for these. We can 
search some given patterns to see if each character matches this enought times. The 
pre-defined patterns are

```{r}
known_patterns
```

Appying these, one character at a time, and seeing which pattern matches the most number 
of characters at a position, we can determine which pattern best fits at that position

```{r}
(guess <- purrr::map(split_by_length(identifiers), detect_pattern, tolerance = 0.9))
```

How many identifiers match these patterns?

```{r}
matches <- purrr::map2(split_by_length(identifiers), guess, ~stringr::str_match(.x, .y))
names(matches) <- guess
matches
```

## Working Prototype

Now that the pieces seem to work, we can apply the categorisations in a function, 
returning (invisibly) a list of matches and non-matches, and printing a summary 
to the screen

```{r}
results <- categorise_regex(identifiers, tolerance = 0.9)
```

where we see the single confounder in each case is not matched.

The actual categorisations are also available

```{r}
results
```


## Yet To Do

- variable-length identifiers
- multiple identifiers with a given length
- most testing
- documentation
